FoRTE Disturbance Paper Analysis

### 2021-06-08 C.analysis/paper_analysis.Rmd
Update manuscript figs

library(dplyr)
library(ggplot2)

@@

```{r}
ED_output %>%  
  filter(scn == "harvest_0" & variable  %in% c("GPP", "NPP", "Rh", "NEP")) %>% 
  mutate(description = paste0(variable, ' (', unit,  ')')) %>% 
  ggplot(aes(year, value, color = met, group = met)) + 
  geom_line() + 
   facet_wrap("description", scales = 'free', strip.position = "top",
             labeller = label_wrap_gen(width = 20, multi_line = TRUE)) +
  THEME +
  labs(y = "")
```

@@

```{r}
ggplot(data = disturbance) + 
  geom_line(aes(year, value, color = severity, line = met), alpha = 0.5) + 
  facet_wrap("variable", scales = 'free') +
  THEME +
  labs(y = "ln(treatment/control)") +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  labs(title = "Disturbance Response")
```

@@

```{r}
ggplot(data = resistance) + 
  geom_point(aes(severity, trough_resistance, color = severity), position = position_jitter(), alpha = 0.5, size = 2) + 
  facet_wrap("variable", scales = "free") + 
  labs(y = "ln(dist/control) unitless", 
       title = "Resistance") + 
  THEME + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS)

@@

```{r}
ggplot(data = resilience) + 
  geom_point(aes(severity, resilience, color = severity), position = position_jitter(), alpha = 0.5, size = 2) + 
  facet_wrap("variable", scales = "free") + 
  labs(y = "ln(dist/control) unitless", 
       title = "Resilience") + 
  THEME + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS)
```

@@

```{r}
resilience %>%
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.5, size = 2) + 
   facet_wrap("variable", scales = "free") + 
  labs(x = "resistance", 
       y = "resilience", 
       title = "Resilience vs. Resistance") + 
  THEME + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS)
```

@@

```{r, fig.width=8, fig.height=8}
annual_met %>% 
  mutate(description = paste0(description, ' (', units, ')')) %>% 
  ggplot(aes(year, value, color = met, group = met)) + 
  geom_line() +
   facet_wrap("description", scales = 'free', strip.position = "top",
             labeller = label_wrap_gen(width = 20, multi_line = TRUE)) +
  THEME +
  labs(y = NULL, x  = NULL,  title = "Annual Met") + 
  theme(legend.position = "none")
```

@@

```{r, fig.width=8, fig.height=8}
monthly_met %>% 
  mutate(description = paste0(description, ' (', units, ')')) %>% 
  ggplot(aes(mon_time, value, color = met, group = met, line = met)) + 
  geom_line() +
   facet_wrap("description", scales = 'free', strip.position = "top",
             labeller = label_wrap_gen(width = 20, multi_line = TRUE)) +
  THEME +
  labs(y = NULL, x  = NULL, title = "Monthly Met") + 
  theme(legend.position = "none")
```

>>>>

library(dplyr)
library(ggplot2)
library(stringr)

@@

```{r, fig.width=6.5, fig.height=4, fig.retina = 4}
ED_output %>%  
  filter(scn == "harvest_0" & variable  %in% c("GPP", "NPP", "Rh", "NEP")) %>% 
  mutate(description = paste0(variable, '\n (', unit,  ')')) %>% 
  ggplot(aes(year, value, group = met,  color = met)) + 
  geom_line() + 
  facet_wrap("description", scales = "free",  
             labeller = label_glue('({.l}) {description}')) + 
  THEME +
  labs(y = "", x = "Year")  + 
  theme(legend.position = "none") -> 
  plot

plot + 
  ggsave("figures/baseline.png", width = 6, height = 4.5)

@@

```{r}
disturbance %>%  
  mutate(Severity = severity) %>% 
  ggplot() + 
  geom_line(aes(year, value, color = Severity, line = met), alpha = 0.5) + 
  facet_wrap("variable", scales = 'free', 
             labeller = label_glue('({.l}) {variable}')) +
  THEME +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  guides(colour = guide_legend("Severity")) + 
  labs(y = "Log Ratio", x = "Years Since Disturbance") -> 
  plot

plot
plot + 
  ggsave("figures/disturbance.png", width = 6, height = 4.5)

@@

```{r, fig.width=5, fig.height=5}
ggplot(data = resistance) + 
  geom_point(aes(severity, trough_resistance, color = severity),
             position = position_jitter(), 
             alpha = 0.75, size = 1.5) + 
  facet_wrap("variable", scales = "free",  
             labeller = label_glue('({.l}) {variable}')) + 
  labs(y = "Log Ratio", 
       title = "Resistance", x = "Severity") + 
  theme_bw(base_size = 10) +
  guides(colour = guide_legend("Severity")) + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS) -> 
  plot

plot + 
  ggsave("figures/resistance.png", width = 6, height = 4.5)

@@

```{r, fig.width=5, fig.height=5}
ggplot(data = resilience) + 
  geom_point(aes(severity, resilience, color = severity),              position = position_jitter(), 
             alpha = 0.75, size = 1.5) + 
  facet_wrap("variable", scales = "free",  
             labeller = label_glue('({.l}) {variable}')) + 
  labs(y = "Log Ratio", 
       title = "Resilience", 
        x = "Severity") + 
  theme_bw(base_size = 10) +
  guides(colour = guide_legend("Severity")) + 
  scale_color_manual(values = FORTE_SEVERITY_COLORS) -> 
  plot

plot + 
  ggsave("figures/resilience.png", width = 6, height = 4.5)
```

@@

```{r, fig.width=5, fig.height=5}
resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  facet_wrap("variable", scales = "free",  
             labeller = label_glue('({.l}) {variable}')) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  guides(colour = guide_legend("Severity")) -> 
  plot

plot + 
  ggsave("figures/resistance_resilience.png", width = 6, height = 4.5)

@@

```{r, fig.width=5, fig.height=5}
annual_met %>% 
  mutate(description = paste0(description, ' (', units, ')')) %>% 
  ggplot(aes(year, value, color = met, group = met)) + 
  geom_line() +
   facet_wrap("description", scales = 'free', strip.position = "top",
             labeller = label_wrap_gen(width = 20, multi_line = TRUE)) +
  THEME +
  labs(y = NULL, x  = NULL,  title = "Annual Met") + 
  theme(legend.position = "none")
```

@@

```{r, fig.width=10, fig.height=5.5}
monthly_met %>% 
  mutate(units = if_else(variable == "vgrd", 'm s-1', units)) %>% 
  mutate(description = paste0(str_to_title(description), '\n(', units, ')')) %>% 
  ggplot(aes(mon_time, value, color = met, group = met, line = met)) + 
  geom_line() +
   facet_wrap("description", scales = 'free', strip.position = "top",
             labeller = label_wrap_gen(width = 20)) +
  labs(y = NULL, x  = NULL) +
  THEME +
  scale_x_continuous(labels = c("Jan", "Jun", "Dec"), breaks = c(1, 6, 12)) +
  theme(legend.position = "none") -> plot

plot + 
  ggsave("figures/monthly_met.png", width = 10, height = 10)
